visitation_bias

### 2021-01-26 code/visitation_bias.Rmd
developed ordination analysis

  no1 <- x %>%
    group_by(bb.sp, !!criterion, site, date) %>% # group by site-year and BB-FL pair
    summarize(visits = sum(visits)) %>%
    group_by(bb.sp, site, date) %>% # group by site-year and BB species
    mutate(prop.visits = visits/sum(visits)) %>% # get proportional interaction frequency for each BB-FL pair
    select(site, date, bb.sp, !!criterion, prop.visits) %>%
    pivot_wider(names_from = !!criterion, values_from = prop.visits, values_fill = 0) %>% # spread into the kind of array vegan likes
    group_by(site, date) %>%
    nest() %>% # nest into list-column
    mutate(data2 = map(data, function(x) column_to_rownames(x, var = "bb.sp")), # column to rownames
           richness = map(data, function(x) length(x$bb.sp)),
           dist = map(data2, function(x) vegdist(x, method = "horn")), # convert to Horn's distance matrix
           tidy_dist = map(dist, tidy)) %>% # convert to tidy array of Horn's distances
    #dplyr::select(site, date, tidy_dist) %>% # drop intermediate list-columns
    unnest(cols = c(tidy_dist)) %>%
    rename(bb.sp1 = item1, bb.sp2 = item2) %>%
    mutate(niche.overlap = 1-distance,  # express niche overlap so that 1 = perfect overlap and 0 = no overlap
           telu = if_else(bb.sp1 == "telu" | bb.sp2 == "telu", TRUE, FALSE),
           pasc = if_else(bb.sp1 == "pasc" | bb.sp2 == "pasc", TRUE, FALSE),
           wurf = if_else(bb.sp1 == "wurf" | bb.sp2 == "wurf", TRUE, FALSE),
           prat = if_else(bb.sp1 == "prat" | bb.sp2 == "prat", TRUE, FALSE),
           soro = if_else(bb.sp1 == "soro" | bb.sp2 == "soro", TRUE, FALSE),
           humi = if_else(bb.sp1 == "humi" | bb.sp2 == "humi", TRUE, FALSE),
           muci = if_else(bb.sp1 == "muci" | bb.sp2 == "muci", TRUE, FALSE),
           pyre = if_else(bb.sp1 == "pyre" | bb.sp2 == "pyre", TRUE, FALSE),
           mont = if_else(bb.sp1 == "mont" | bb.sp2 == "mont", TRUE, FALSE),
           mend = if_else(bb.sp1 == "mend" | bb.sp2 == "mend", TRUE, FALSE),
           psit = if_else(bb.sp1 == "psit" | bb.sp2 == "psit", TRUE, FALSE),
           gers = if_else(bb.sp1 == "gers" | bb.sp2 == "gers", TRUE, FALSE),
           jone = if_else(bb.sp1 == "jone" | bb.sp2 == "jone", TRUE, FALSE),
           hypn = if_else(bb.sp1 == "hypn" | bb.sp2 == "hypn", TRUE, FALSE),
           lapi = if_else(bb.sp1 == "lapi" | bb.sp2 == "lapi", TRUE, FALSE),
           hort = if_else(bb.sp1 == "hort" | bb.sp2 == "hort", TRUE, FALSE))
}
```

### 3.1.2 My first question is how niche overlap compares across species pairs
```{r}
# Unaggregated niche overlap per species pair; not that this drops a lot of data because of the inner join with bias
niche_overlap <- read_csv("../data/processed_data/network.csv") %>%
  filter(caste != "male") %>% # we will ignore males 
  group_by(site, date, bb.sp, plant.sp) %>%
  summarize(visits = n()) %>%
  niche_overlapper(plant.sp) %>%
  mutate(yday = yday(date)) %>%
  left_join(bb_traits, by = c("bb.sp1" = "bb.sp")) %>%
  rename(pbl.w.class2_sp1 = pbl.w.class2) %>%
  left_join(bb_traits, by = c("bb.sp2" = "bb.sp")) %>%
  rename(pbl.w.class2_sp2 = pbl.w.class2) %>%
  mutate(same.class = case_when(
    pbl.w.class2_sp1 == "1" & pbl.w.class2_sp2 == "1" ~ "short:short",
    pbl.w.class2_sp1 == "2" & pbl.w.class2_sp2 == "2" ~ "med:med",
    pbl.w.class2_sp1 == "3" & pbl.w.class2_sp2 == "3" ~ "long:long",
    pbl.w.class2_sp1 == "1" & pbl.w.class2_sp2 == "2" ~ "short:med",
    pbl.w.class2_sp1 == "2" & pbl.w.class2_sp2 == "1" ~ "short:med",
    pbl.w.class2_sp1 == "1" & pbl.w.class2_sp2 == "3" ~ "short:long",
    pbl.w.class2_sp1 == "3" & pbl.w.class2_sp2 == "1" ~ "short:long",
    pbl.w.class2_sp1 == "2" & pbl.w.class2_sp2 == "3" ~ "med:long",
    pbl.w.class2_sp1 == "3" & pbl.w.class2_sp2 == "2" ~ "med:long")
    ) %>%
  left_join(bb_abundance, by = c("site", "date", "bb.sp1" = "bb.sp")) %>%
  rename(bb.sp1.abund = bb.sp.abund) %>%
  left_join(bb_abundance, by = c("site", "date", "bb.sp2" = "bb.sp")) %>%
  rename(bb.sp2.abund = bb.sp.abund) %>%
  unite(sp.pair, c(bb.sp1, bb.sp2), sep = "_", remove = FALSE) %>%
  left_join(site_data) %>%
  mutate(yday = yday(date)) %>%
  select(site, date, yday, elev.mean, sp.pair, bb.sp1, bb.sp2, bb.sp1.abund, 
         bb.sp2.abund, niche.overlap, same.class)

@@

@@

@@

# Now a threshold of 5...bye, all the species pairs...
ggplot(filter(niche_overlap, bb.sp1.abund >= 5 & bb.sp1.abund >= 5), 
       aes(sp.pair, niche.overlap)) +
  geom_violin() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(filter(niche_overlap, bb.sp1.abund >= 10 & bb.sp1.abund >= 10), 
       aes(sp.pair, niche.overlap)) +
  geom_violin() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

@@

# Now for what is probably a pretty naive model

brm_niche00 <- brm(niche.overlap ~ bb.sp1.abund*bb.sp2.abund + 
                     (1 | sp.pair) + 
                     (1 | same.class) + 
                     (1 | site),
                   chains = 4,
                   cores = 4,
                   iter = 2000,
                   file = "../output/brm_niche00",
                   data = filter(niche_overlap, bb.sp1.abund >= 1 & bb.sp1.abund >= 1))

@@

### 3.1.3 Now I'd be interested to know how niche overlap relates to dprime
```{r}
niche_overlap_bias <- niche_overlap %>%
  inner_join(bias, by = c("site", "date", c("bb.sp1" = "bb.sp"))) %>%
  rename(dprime.sp1 = dprime.sp) %>%
  inner_join(bias, by = c("site", "date", c("bb.sp2" = "bb.sp"))) %>%
  rename(dprime.sp2 = dprime.sp) %>%
  select(site, date, bb.sp1, bb.sp2, bb.sp1.abund, bb.sp2.abund, 
         dprime.sp1, dprime.sp2, niche.overlap, same.class)

# When bias is high, it could mean that there are few good options on which all (or many) BB species converge. But apparently it doesn't. When bias is high, BB spp are biased toward DIFFERENT flora, and thus their niches diverge. 
ggplot(niche_overlap_bias, aes(dprime.sp, mean.niche.overlap)) +
  geom_point(alpha = 0.1) +
  geom_smooth(method = "lm") +
  #geom_smooth(method = "gam", formula = y ~ s(x, k = 5), se = TRUE) +
  facet_wrap(~bb.sp) +
  ylim(c(0,1))

>>>>

  no1 <- x %>%
    group_by(bb.sp, !!criterion, site, date) %>% # group by site-year and BB-FL pair
    summarize(visits = sum(visits)) %>%
    group_by(bb.sp, site, date) %>% # group by site-year and BB species
    mutate(prop.visits = visits/sum(visits)) %>% # get proportional interaction frequency for each BB-FL pair
    select(site, date, bb.sp, !!criterion, prop.visits) %>%
    pivot_wider(names_from = !!criterion, values_from = prop.visits, values_fill = 0) %>% # spread into the kind of array vegan likes
    group_by(site, date) %>%
    nest() %>% # nest into list-column
    mutate(data2 = map(data, function(x) column_to_rownames(x, var = "bb.sp")), # column to rownames
           richness = map(data, function(x) length(x$bb.sp)),
           dist = map(data2, function(x) vegdist(x, method = "horn")), # convert to Horn's distance matrix
           tidy_dist = map(dist, tidy)) %>% # convert to tidy array of Horn's distances
    #dplyr::select(site, date, tidy_dist) %>% # drop intermediate list-columns
    unnest(cols = c(tidy_dist)) %>%
    rename(bb.sp1 = item1, bb.sp2 = item2) %>%
    mutate(niche.overlap = 1-distance,  # express niche overlap so that 1 = perfect overlap and 0 = no overlap
           telu = if_else(bb.sp1 == "telu" | bb.sp2 == "telu", TRUE, FALSE),
           pasc = if_else(bb.sp1 == "pasc" | bb.sp2 == "pasc", TRUE, FALSE),
           wurf = if_else(bb.sp1 == "wurf" | bb.sp2 == "wurf", TRUE, FALSE),
           prat = if_else(bb.sp1 == "prat" | bb.sp2 == "prat", TRUE, FALSE),
           soro = if_else(bb.sp1 == "soro" | bb.sp2 == "soro", TRUE, FALSE),
           humi = if_else(bb.sp1 == "humi" | bb.sp2 == "humi", TRUE, FALSE),
           muci = if_else(bb.sp1 == "muci" | bb.sp2 == "muci", TRUE, FALSE),
           pyre = if_else(bb.sp1 == "pyre" | bb.sp2 == "pyre", TRUE, FALSE),
           mont = if_else(bb.sp1 == "mont" | bb.sp2 == "mont", TRUE, FALSE),
           mend = if_else(bb.sp1 == "mend" | bb.sp2 == "mend", TRUE, FALSE),
           psit = if_else(bb.sp1 == "psit" | bb.sp2 == "psit", TRUE, FALSE),
           gers = if_else(bb.sp1 == "gers" | bb.sp2 == "gers", TRUE, FALSE),
           jone = if_else(bb.sp1 == "jone" | bb.sp2 == "jone", TRUE, FALSE),
           hypn = if_else(bb.sp1 == "hypn" | bb.sp2 == "hypn", TRUE, FALSE),
           lapi = if_else(bb.sp1 == "lapi" | bb.sp2 == "lapi", TRUE, FALSE),
           hort = if_else(bb.sp1 == "hort" | bb.sp2 == "hort", TRUE, FALSE))
}

# Aggregating over site
niche_overlapper2 <- function(x, criterion) {

  no1 <- x %>%
    group_by(bb.sp, !!criterion, site) %>% # group by site-year and BB-FL pair
    summarize(visits = sum(visits)) %>%
    group_by(bb.sp, site) %>% # group by site-year and BB species
    mutate(prop.visits = visits/sum(visits)) %>% # get proportional interaction frequency for each BB-FL pair
    select(site, bb.sp, !!criterion, prop.visits) %>%
    pivot_wider(names_from = !!criterion, values_from = prop.visits, values_fill = 0) %>% # spread into the kind of array vegan likes
    group_by(site) %>%
    nest() %>% # nest into list-column
    mutate(data2 = map(data, function(x) column_to_rownames(x, var = "bb.sp")), # column to rownames
           richness = map(data, function(x) length(x$bb.sp)),
           dist = map(data2, function(x) vegdist(x, method = "horn")), # convert to Horn's distance matrix
           tidy_dist = map(dist, tidy)) %>% # convert to tidy array of Horn's distances
    #dplyr::select(site, date, tidy_dist) %>% # drop intermediate list-columns
    unnest(cols = c(tidy_dist)) %>%
    rename(bb.sp1 = item1, bb.sp2 = item2) %>%
    mutate(niche.overlap = 1-distance,  # express niche overlap so that 1 = perfect overlap and 0 = no overlap
           telu = if_else(bb.sp1 == "telu" | bb.sp2 == "telu", TRUE, FALSE),
           pasc = if_else(bb.sp1 == "pasc" | bb.sp2 == "pasc", TRUE, FALSE),
           wurf = if_else(bb.sp1 == "wurf" | bb.sp2 == "wurf", TRUE, FALSE),
           prat = if_else(bb.sp1 == "prat" | bb.sp2 == "prat", TRUE, FALSE),
           soro = if_else(bb.sp1 == "soro" | bb.sp2 == "soro", TRUE, FALSE),
           humi = if_else(bb.sp1 == "humi" | bb.sp2 == "humi", TRUE, FALSE),
           muci = if_else(bb.sp1 == "muci" | bb.sp2 == "muci", TRUE, FALSE),
           pyre = if_else(bb.sp1 == "pyre" | bb.sp2 == "pyre", TRUE, FALSE),
           mont = if_else(bb.sp1 == "mont" | bb.sp2 == "mont", TRUE, FALSE),
           mend = if_else(bb.sp1 == "mend" | bb.sp2 == "mend", TRUE, FALSE),
           psit = if_else(bb.sp1 == "psit" | bb.sp2 == "psit", TRUE, FALSE),
           gers = if_else(bb.sp1 == "gers" | bb.sp2 == "gers", TRUE, FALSE),
           jone = if_else(bb.sp1 == "jone" | bb.sp2 == "jone", TRUE, FALSE),
           hypn = if_else(bb.sp1 == "hypn" | bb.sp2 == "hypn", TRUE, FALSE),
           lapi = if_else(bb.sp1 == "lapi" | bb.sp2 == "lapi", TRUE, FALSE),
           hort = if_else(bb.sp1 == "hort" | bb.sp2 == "hort", TRUE, FALSE))
}

niche_overlapper3 <- function(x, criterion) {

  no1 <- x %>%
    group_by(bb.sp, !!criterion, site) %>% # group by site-year and BB-FL pair
    summarize(visits = sum(visits)) %>%
    select(site, bb.sp, !!criterion, visits) %>%
    pivot_wider(names_from = !!criterion, values_from = visits, values_fill = 0) %>% # spread into the kind of array vegan likes
    group_by(site) %>%
    nest() %>% # nest into list-column
    mutate(data2 = map(data, function(x) column_to_rownames(x, var = "bb.sp")), # column to rownames
           richness = map(data, function(x) length(x$bb.sp)),
           dist = map(data2, function(x) vegdist(x, method = "horn")), # convert to Horn's distance matrix
           tidy_dist = map(dist, tidy)) %>% # convert to tidy array of Horn's distances
    #dplyr::select(site, date, tidy_dist) %>% # drop intermediate list-columns
    unnest(cols = c(tidy_dist)) %>%
    rename(bb.sp1 = item1, bb.sp2 = item2) %>%
    mutate(niche.overlap = 1-distance,  # express niche overlap so that 1 = perfect overlap and 0 = no overlap
           telu = if_else(bb.sp1 == "telu" | bb.sp2 == "telu", TRUE, FALSE),
           pasc = if_else(bb.sp1 == "pasc" | bb.sp2 == "pasc", TRUE, FALSE),
           wurf = if_else(bb.sp1 == "wurf" | bb.sp2 == "wurf", TRUE, FALSE),
           prat = if_else(bb.sp1 == "prat" | bb.sp2 == "prat", TRUE, FALSE),
           soro = if_else(bb.sp1 == "soro" | bb.sp2 == "soro", TRUE, FALSE),
           humi = if_else(bb.sp1 == "humi" | bb.sp2 == "humi", TRUE, FALSE),
           muci = if_else(bb.sp1 == "muci" | bb.sp2 == "muci", TRUE, FALSE),
           pyre = if_else(bb.sp1 == "pyre" | bb.sp2 == "pyre", TRUE, FALSE),
           mont = if_else(bb.sp1 == "mont" | bb.sp2 == "mont", TRUE, FALSE),
           mend = if_else(bb.sp1 == "mend" | bb.sp2 == "mend", TRUE, FALSE),
           psit = if_else(bb.sp1 == "psit" | bb.sp2 == "psit", TRUE, FALSE),
           gers = if_else(bb.sp1 == "gers" | bb.sp2 == "gers", TRUE, FALSE),
           jone = if_else(bb.sp1 == "jone" | bb.sp2 == "jone", TRUE, FALSE),
           hypn = if_else(bb.sp1 == "hypn" | bb.sp2 == "hypn", TRUE, FALSE),
           lapi = if_else(bb.sp1 == "lapi" | bb.sp2 == "lapi", TRUE, FALSE),
           hort = if_else(bb.sp1 == "hort" | bb.sp2 == "hort", TRUE, FALSE))
}
```

### 3.1.2 My first question is how niche overlap compares across species pairs
#### 3.1.2.1 Calculate pairwise niche overlap
```{r}
# Get bb.sp abundances; this time without filtering out the sites without matching floral data
bb_abundance2 <-  read_csv("../data/processed_data/network.csv") %>%
  filter(caste != "male") %>% # we will ignore males 
  group_by(site, date, bb.sp, plant.sp) %>%
  summarize(visits = n()) %>%
  group_by(site, date, bb.sp) %>%
  summarize(bb.sp.abund = sum(visits)) %>%
  group_by(site, date) %>%
  mutate(bb.sp.prop.abund = bb.sp.abund/sum(bb.sp.abund))

bb_abundance2_agg <-  read_csv("../data/processed_data/network.csv") %>%
  filter(caste != "male") %>% # we will ignore males 
  group_by(site, bb.sp, plant.sp) %>%
  summarize(visits = n()) %>%
  group_by(site, bb.sp) %>%
  summarize(bb.sp.abund = sum(visits)) %>%
  group_by(site) %>%
  mutate(bb.sp.prop.abund = bb.sp.abund/sum(bb.sp.abund))

# Un-aggregated niche overlap per species pair per site-date
niche_overlap <- read_csv("../data/processed_data/network.csv") %>%
  filter(caste != "male") %>% # we will ignore males 
  group_by(site, date, bb.sp, plant.sp) %>%
  summarize(visits = n()) %>%
  niche_overlapper(plant.sp) %>%
  mutate(yday = yday(date)) %>%
  left_join(bb_traits, by = c("bb.sp1" = "bb.sp")) %>%
  rename(pbl.w.class2_sp1 = pbl.w.class2) %>%
  left_join(bb_traits, by = c("bb.sp2" = "bb.sp")) %>%
  rename(pbl.w.class2_sp2 = pbl.w.class2) %>%
  mutate(same.class = case_when(
    pbl.w.class2_sp1 == "1" & pbl.w.class2_sp2 == "1" ~ "short:short",
    pbl.w.class2_sp1 == "2" & pbl.w.class2_sp2 == "2" ~ "med:med",
    pbl.w.class2_sp1 == "3" & pbl.w.class2_sp2 == "3" ~ "long:long",
    pbl.w.class2_sp1 == "1" & pbl.w.class2_sp2 == "2" ~ "short:med",
    pbl.w.class2_sp1 == "2" & pbl.w.class2_sp2 == "1" ~ "short:med",
    pbl.w.class2_sp1 == "1" & pbl.w.class2_sp2 == "3" ~ "short:long",
    pbl.w.class2_sp1 == "3" & pbl.w.class2_sp2 == "1" ~ "short:long",
    pbl.w.class2_sp1 == "2" & pbl.w.class2_sp2 == "3" ~ "med:long",
    pbl.w.class2_sp1 == "3" & pbl.w.class2_sp2 == "2" ~ "med:long")
    ) %>%
  left_join(bb_abundance2, by = c("site", "date", "bb.sp1" = "bb.sp")) %>%
  rename(bb.sp1.abund = bb.sp.abund) %>%
  left_join(bb_abundance2, by = c("site", "date", "bb.sp2" = "bb.sp")) %>%
  rename(bb.sp2.abund = bb.sp.abund) %>%
  unite(sp.pair, c(bb.sp1, bb.sp2), sep = "_", remove = FALSE) %>%
  left_join(site_data) %>%
  mutate(yday = yday(date)) %>%
  select(site, date, yday, elev.mean, sp.pair, bb.sp1, bb.sp2, bb.sp1.abund, 
         bb.sp2.abund, niche.overlap, same.class) %>%
  mutate(log.bb.sp1.abund = log(bb.sp1.abund),
         log.bb.sp2.abund = log(bb.sp2.abund))

# Aggregated niche overlap per species pair per site
niche_overlap2 <- read_csv("../data/processed_data/network.csv") %>%
  filter(caste != "male") %>% # we will ignore males 
  group_by(site, bb.sp, plant.sp) %>%
  summarize(visits = n()) %>%
  niche_overlapper2(plant.sp) %>%
  left_join(bb_traits, by = c("bb.sp1" = "bb.sp")) %>%
  rename(pbl.w.class2_sp1 = pbl.w.class2) %>%
  left_join(bb_traits, by = c("bb.sp2" = "bb.sp")) %>%
  rename(pbl.w.class2_sp2 = pbl.w.class2) %>%
  mutate(same.class = case_when(
    pbl.w.class2_sp1 == "1" & pbl.w.class2_sp2 == "1" ~ "short:short",
    pbl.w.class2_sp1 == "2" & pbl.w.class2_sp2 == "2" ~ "med:med",
    pbl.w.class2_sp1 == "3" & pbl.w.class2_sp2 == "3" ~ "long:long",
    pbl.w.class2_sp1 == "1" & pbl.w.class2_sp2 == "2" ~ "short:med",
    pbl.w.class2_sp1 == "2" & pbl.w.class2_sp2 == "1" ~ "short:med",
    pbl.w.class2_sp1 == "1" & pbl.w.class2_sp2 == "3" ~ "short:long",
    pbl.w.class2_sp1 == "3" & pbl.w.class2_sp2 == "1" ~ "short:long",
    pbl.w.class2_sp1 == "2" & pbl.w.class2_sp2 == "3" ~ "med:long",
    pbl.w.class2_sp1 == "3" & pbl.w.class2_sp2 == "2" ~ "med:long")
    ) %>%
  left_join(bb_abundance2_agg, by = c("site", "bb.sp1" = "bb.sp")) %>%
  rename(bb.sp1.abund = bb.sp.abund) %>%
  left_join(bb_abundance2_agg, by = c("site", "bb.sp2" = "bb.sp")) %>%
  rename(bb.sp2.abund = bb.sp.abund) %>%
  unite(sp.pair, c(bb.sp1, bb.sp2), sep = "_", remove = FALSE) %>%
  left_join(site_data) %>%
  select(site, elev.mean, sp.pair, bb.sp1, bb.sp2, bb.sp1.abund, 
         bb.sp2.abund, niche.overlap, same.class) %>%
  mutate(log.bb.sp1.abund = log(bb.sp1.abund),
         log.bb.sp2.abund = log(bb.sp2.abund))

write_csv(niche_overlap2, "../hpc_packets/niche_overlap2.csv")
```

#### 3.1.2.2 Preliminary visualization
```{r}
ggplot(niche_overlap, aes(bb.sp1.abund, bb.sp2.abund, color = niche.overlap)) +
  geom_point()

ggplot(niche_overlap, aes(bb.sp1.abund, niche.overlap)) +
  geom_point() +
  geom_smooth(method = "gam", formula = y ~ s(x, k = 4))

ggplot(niche_overlap, aes(bb.sp2.abund, niche.overlap)) +
  geom_point() +
  geom_smooth(method = "gam", formula = y ~ s(x, k = 4))

ggplot(niche_overlap, aes(log.bb.sp1.abund, niche.overlap)) +
  geom_point() +
  geom_smooth(method = "gam", formula = y ~ s(x, k = 4))

ggplot(niche_overlap, aes(log.bb.sp2.abund, niche.overlap)) +
  geom_point() +
  geom_smooth(method = "gam", formula = y ~ s(x, k = 4))

ggplot(niche_overlap, aes(log.bb.sp2.abund, niche.overlap, color = same.class)) +
  geom_point() +
  geom_smooth(method = "gam", formula = y ~ s(x, k = 4))

ggplot(niche_overlap, aes(sqrt(bb.sp2.abund), sqrt(niche.overlap), color = same.class)) +
  geom_point() +
  geom_smooth(method = "gam", formula = y ~ s(x, k = 4))

ggplot(niche_overlap, aes(bb.sp2.abund, niche.overlap, color = same.class)) +
  geom_point() +
  geom_smooth(method = "gam", formula = y ~ s(x, k = 4))

ggplot(niche_overlap, aes(log.bb.sp1.abund, log.bb.sp2.abund, color = niche.overlap)) +
  geom_point()

@@

ggplot(niche_overlap, aes(same.class, niche.overlap)) +
  geom_violin() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

@@

ggplot(filter(niche_overlap, bb.sp1.abund >= 2 & bb.sp1.abund >= 2), 
       aes(same.class, niche.overlap)) +
  geom_violin() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

@@

# Now a threshold of 5...bye, all the species pairs...
ggplot(filter(niche_overlap, bb.sp1.abund >= 5 & bb.sp1.abund >= 5), 
       aes(same.class, niche.overlap)) +
  geom_violin() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(filter(niche_overlap, bb.sp1.abund >= 10 & bb.sp1.abund >= 10), 
       aes(same.class, niche.overlap)) +
  geom_violin() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

@@

ggplot(niche_overlap, aes(sp.pair, niche.overlap)) +
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Aggregate by site
ggplot(niche_overlap2, aes(bb.sp1.abund, niche.overlap)) +
  geom_point() +
  geom_smooth(method = "gam", formula = y ~ s(x, k = 5))

ggplot(niche_overlap2, aes(log.bb.sp1.abund, niche.overlap)) +
  geom_point() +
  geom_smooth(method = "gam", formula = y ~ s(x, k = 5))

ggplot(niche_overlap2, aes(log.bb.sp1.abund, niche.overlap)) +
  geom_point() +
  geom_smooth(method = "gam", formula = y ~ s(x, k = 5)) +
  facet_wrap(~same.class)

ggplot(niche_overlap2, aes(log.bb.sp1.abund, niche.overlap)) +
  geom_point() +
  geom_smooth(method = "gam", formula = y ~ s(x, k = 5)) +
  facet_wrap(~sp.pair)

ggplot(niche_overlap2, aes(sp.pair, niche.overlap)) +
  geom_violin() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(niche_overlap2, aes(sp.pair, niche.overlap)) +
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(niche_overlap2, aes(same.class, niche.overlap)) +
  geom_violin() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(niche_overlap2, aes(elev.mean, niche.overlap)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  facet_wrap(~sp.pair)

ggplot(niche_overlap, aes(niche.overlap)) +
  geom_histogram() +
  facet_wrap(~sp.pair)

## raw visits aggregate
ggplot(niche_overlap3, aes(log.bb.sp1.abund, niche.overlap)) +
  geom_point() +
  geom_smooth(method = "gam", formula = y ~ s(x, k = 5))

ggplot(niche_overlap3, aes(same.class, niche.overlap)) +
  geom_violin() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(niche_overlap2, aes(niche.overlap)) +
  geom_histogram() +
  facet_wrap(~sp.pair)

#### 3.1.2.3 brms model ... still a mess
```{r}
brm_niche00 <- brm(niche.overlap ~ bb.sp1.abund*bb.sp2.abund + 
                     (1 | sp.pair) + 
                     (1 | same.class) + 
                     (1 | site),
                   control = list(adapt_delta = 0.90),
                   chains = 4,
                   cores = 4,
                   iter = 2000,
                   file = "../output/brm_niche00",
                   data = niche_overlap)

parnames(brm_niche00)
conditional_effects(brm_niche00)
mcmc_plot(brm_niche00, pars = c("^r_sp"))
mcmc_plot(brm_niche00, pars = c("^r_sa"))
mcmc_plot(brm_niche00, pars = c("^b_"))
hypothesis(brm_niche00, "dprime = 0")
pp_check(brm_niche00)
bayes_R2(brm_niche00)

# To stabilize niche overlap (avoid lots of  1s and 0s), we will filter the data to include only species pairs in which both species were represented by at least 3 observations.
brm_niche01 <- brm(niche.overlap ~ bb.sp1.abund*bb.sp2.abund + 
                     (1 | sp.pair) + 
                     (1 | same.class) + 
                     (1 | site),
                   chains = 4,
                   cores = 4,
                   iter = 2000,
                   file = "../output/brm_niche01",
                   data = filter(niche_overlap, bb.sp1.abund >= 2 & bb.sp1.abund >= 2))

parnames(brm_niche01)
conditional_effects(brm_niche01)
mcmc_plot(brm_niche01, pars = c("^r_sp"))
mcmc_plot(brm_niche01, pars = c("^r_sa"))
mcmc_plot(brm_niche01, pars = c("^b_"))
hypothesis(brm_niche01, "dprime = 0")
pp_check(brm_niche01)
bayes_R2(brm_niche01)

# Would it help if we log-transformed the bb abundance data and stuck to unfiltered data?
brm_niche02 <- brm(niche.overlap ~ log.bb.sp1.abund*log.bb.sp2.abund + 
                     (1 | sp.pair) + 
                     (1 | same.class) + 
                     (1 | site),
                   #control = list(adapt_delta = 0.90),
                   chains = 4,
                   cores = 4,
                   iter = 2000,
                   file = "../output/brm_niche02",
                   data = niche_overlap)

@@

brm_niche03 <- brm(niche.overlap ~ log.bb.sp1.abund*log.bb.sp2.abund + 
                     (1 + log.bb.sp1.abund*log.bb.sp2.abund | sp.pair) + 
                     (1 | same.class) + 
                     (1 | site),
                   #control = list(adapt_delta = 0.90),
                   chains = 4,
                   cores = 4,
                   iter = 2000,
                   file = "../output/brm_niche03",
                   data = niche_overlap)

# A zero-one inflated model might be the key.
brm_niche04 <- brm(niche.overlap ~ log.bb.sp1.abund*log.bb.sp2.abund + 
                     (1 | sp.pair) + 
                     (1 | same.class) + 
                     (1 | site),
                   #control = list(adapt_delta = 0.90),
                   family = "zero_one_inflated_beta",
                   chains = 4,
                   cores = 4,
                   iter = 2000,
                   file = "../output/brm_niche04",
                   data = niche_overlap)

parnames(brm_niche04)
conditional_effects(brm_niche04)
mcmc_plot(brm_niche04, pars = c("^r_sp"))
mcmc_plot(brm_niche04, pars = c("^r_sa"))
mcmc_plot(brm_niche04, pars = c("^b_"))
hypothesis(brm_niche04, "dprime = 0")
pp_check(brm_niche04)
bayes_R2(brm_niche04)

# Aggregate models
brm_niche60 <- brm(niche.overlap ~ log.bb.sp1.abund*log.bb.sp2.abund + 
                     (1 | sp.pair) + 
                     (1 | same.class) +
                     (1 | site),
                   family = "zero_one_inflated_beta",
                   chains = 4,
                   cores = 4,
                   iter = 2000,
                   file = "../output/brm_niche60",
                   data = niche_overlap2)

parnames(brm_niche60)
conditional_effects(brm_niche60)
mcmc_plot(brm_niche60, pars = c("^r_sp"))
mcmc_plot(brm_niche60, pars = c("^r_sa"))
mcmc_plot(brm_niche60, pars = c("^b_Int"))
hypothesis(brm_niche60, "dprime = 0")
pp_check(brm_niche60)
bayes_R2(brm_niche60)

brm_niche61 <- brm(niche.overlap ~ log.bb.sp1.abund*log.bb.sp2.abund + 
                     (1 | sp.pair) + 
                     (1 | same.class) +
                     (1 | site),
                   control = list(adapt_delta = 0.99),
                   family = "zero_one_inflated_beta",
                   chains = 4,
                   cores = 4,
                   iter = 2000,
                   file = "../output/brm_niche61", # for local
                   #file = "./output/brm_niche61", # for HPC
                   data = niche_overlap2)

parnames(brm_niche61)
conditional_effects(brm_niche61)
mcmc_plot(brm_niche61, pars = c("^r_sp"))
mcmc_plot(brm_niche61, pars = c("^r_sa"))
mcmc_plot(brm_niche61, pars = c("^b_Int"))
pp_check(brm_niche61)
bayes_R2(brm_niche61)

brm_niche62 <- brm(niche.overlap ~ log.bb.sp1.abund*log.bb.sp2.abund + 
                     (1 + log.bb.sp1.abund*log.bb.sp2.abund | sp.pair) + 
                     (1 | same.class) +
                     (1 | site),
                   control = list(adapt_delta = 0.99),
                   family = "zero_one_inflated_beta",
                   chains = 4,
                   cores = 4,
                   iter = 2000,
                   #file = "../output/brm_niche62", # for local
                   file = "./output/brm_niche62", # for HPC
                   data = niche_overlap2)
```

#### 3.2.2.4 Plot model
```{r}
## Sp.pair and same class, for convenience
sp_pair_class <- niche_overlap2 %>%
  ungroup() %>%
  select(sp.pair, same.class) %>%
  distinct()

## Tongue length combos
brm_niche61_plotframe1 <- brm_niche61 %>%
  spread_draws(b_Intercept, r_same.class[condition, term]) %>% 
  mutate(condition_mean = b_Intercept + r_same.class)

ggplot(brm_niche61_plotframe1, aes(condition_mean, reorder(condition, condition_mean))) +
  stat_halfeye() +
  ylab("Tongue length combination") +
  xlab("Niche overlap")

ggsave(file = "../output/brm_niche61_plot1.png", width = 7, height = 5.5)

## Species pairs
brm_niche61_plotframe2 <- brm_niche61 %>%
  spread_draws(b_Intercept, r_sp.pair[condition, term]) %>% 
  mutate(condition_mean = b_Intercept + r_sp.pair) %>%
  left_join(sp_pair_class, by = c("condition" = "sp.pair"))

ggplot(brm_niche61_plotframe2, aes(condition_mean, 
                                   reorder(condition, condition_mean), 
                                   color = same.class)) +
  stat_pointinterval() +
  ylab("Species pair") +
  xlab("Niche overlap")

ggsave(file = "../output/brm_niche61_plot1.png", width = 7, height = 5.5)
```

### 3.1.3 Now I'd be interested to know how niche overlap relates to dprime
```{r}
niche_overlap_bias <- niche_overlap %>%
  inner_join(bias, by = c("site", "date", c("bb.sp1" = "bb.sp"))) %>%
  rename(dprime.sp1 = dprime.sp) %>%
  inner_join(bias, by = c("site", "date", c("bb.sp2" = "bb.sp"))) %>%
  rename(dprime.sp2 = dprime.sp) %>%
  select(site, date, sp.pair, bb.sp1, bb.sp2, bb.sp1.abund, bb.sp2.abund, 
         dprime.sp1, dprime.sp2, niche.overlap, same.class)

# When bias is high, it could mean that there are few good options on which all (or many) BB species converge. But apparently it doesn't. When bias is high, BB spp are biased toward DIFFERENT flora, and thus their niches diverge. 
ggplot(niche_overlap_bias, aes(dprime.sp, mean.niche.overlap)) +
  geom_point(alpha = 0.1) +
  geom_smooth(method = "lm") +
  #geom_smooth(method = "gam", formula = y ~ s(x, k = 5), se = TRUE) +
  facet_wrap(~sp.pair) +
  ylim(c(0,1))
